Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-12-22 paper.tex
Add figure of assumed density along trajectory

The matter potential along this test ray is from an analytic wind
model qualitatively consistent with the densities in the
simulated volume (i.e.\ inside $r\sim70$~km).

>>>>

The matter potential along this test ray is from an analytic wind
model qualitatively consistent with the densities in the
simulated volume (i.e.\ inside $r\sim70$~km) and asymptoting to the $r^{-3}$
density field of a spherical steady-state wind.
\footnote{TODO: confirm whether this is accurate}
The rest density from this model is plotted in Fig.~\ref{fig:test_traj_density}.
\footnote{TODO: cite Surman \& McLaughlin ApJ 618, 2005}

\begin{figure}
  \includegraphics[width=\columnwidth]{profile-density-000Mo-025deg}
  % Plot:    $DIR/RunBA/RunBA-025deg-noscat-production01/profile-density-000Mo-025deg.pdf
  % Script:  $DIR/nu_potentials-production.nb
  % Configs: $DIR/nu_potentials-wind_model.nb
  %          $DIR/RunBA/RunBA-025deg-noscat-production01/nu_potentials-config-production.nb
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20170412-self_interaction_potentials_M12_M12-LS220-M1/Run03/
  \caption{Assumed matter density along the neutrino test trajectory
    used to calculate the matter potential $V_e$.
    }
  \label{fig:test_traj_density}
\end{figure}
